NFC and burnout in teachers - A replication and extension study

### 2022-02-14 Manuscript/Manuscript.Rmd
fixed knitting

keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
wordcount         : "X"
bibliography      : NFC_Burnout.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : apa.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage{chngcntr}
---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}

@@

  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor")

@@

  # those two libraries come from packages with different names, so we load them individually

  library(GGally)                 # from ggplot2, for multi-correlation plots
  library(apa)                    # from the remotes package

@@

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by the findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and wellbeing, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
Only a balance of resources and demands results in personal wellbeing, while an imbalance threatens wellbeing, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery [@Salanova2006].
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (DTH), demands that are too low for one’s personal resources (DTL), and a balanced fit of demands and resources (DRF).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with DTH and negatively associated with DRF.
However, we had no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.

@@

## Material
All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The Covid-19 items can be found in the *Supplementary Material S1*.
The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] cannot be used, so we cannot replicate the mediation of NFC and burnout by active and passive coping.

## Procedure
The questionnaires were provided online using SoSci Survey [@Leiner2019].
Participants were informed about aims and duration of the study and data security, then they provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.

@@

    desc_table <-
      kbl(desc_met,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

@@

  corr_table <-
  kbl(correlations,
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

Basic metric descriptives of the questionnaire scores and subscales are listed in Table 1.
Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].

@@

Correlations and internal consistencies are displayed in Table 2.
For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman"), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman"), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman"), format = "rmarkdown")`).
The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

@@

  replic_table <-
    kbl(replic_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Replication of Grass et al. (2018)"}

@@

  replic_figure <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
                       edge.label.cex = 1, esize = 2, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

In order to replicate findings by Grass et al. [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al. [-@Grass2018].

@@

  replic_years_table <-
    kbl(replic_years_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 9, 11) %>%
    pack_rows("Total Effect", 12, 12) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```

Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
We placed this variable as an independent variable influencing self control, as the latter was the only variable in the model that showed a partial correlation with years spent teaching.
As it was not preregistered, this was an exploratory analysis.
Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI=$ `r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates, total, direct, and indirect effects are displayed and listed in *Supplementary Material S3*.
The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).

@@

@@

>>>>

keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
wordcount         : "~ 5600"
bibliography      : NFC_Burnout.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : apa.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage{chngcntr}
---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\counterwithout{table}{section}
\setcounter{figure}{0}
\setcounter{table}{0}

@@

  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor", "stats", "apa", "GGally")

@@

@@

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active coping, and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regards to stress assessment (how the situation is appraised) and with regards to both coping and recovery [@Salanova2006].
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (DTH), demands that are too low for one’s personal resources (DTL), and a balanced fit of demands and resources (DRF).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with DTH, positively associated with DTL, and positively associated with DRF.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with DTH and negatively associated with DRF.
However, we had no hypothesis regarding the association of DTL and burnout, because even though DTL is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.

@@

## Material
All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI) [@Buessing1992], NFC using the 16-item Need for Cognition Scale (NCS) [@Bless1994], self-control using the 13-item Self-Control Scale (SCS) [@Bertrams2009a], reappraisal and suppression using the 10-item Emotion Regulation Questionnaire (ERQ) [@Abler2009], and work satisfaction using the Allgemeine Arbeitszufriedenheit questionnaire [@Fischer2014].
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The translated Covid-19 items can be found in the *Supplementary Material S1*.
The survey also included the Subjective Wellbeing Index of the World Health Organization [@Braehler2007], which we will not analyze.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar [@BoehmKasper2001] could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.

## Procedure
The questionnaires were provided online using SoSci Survey [@Leiner2019].
Participants were informed about aims and duration of the study and data security, provided demographic information, answered the questionnaires, and could optionally enter their email address to be informed about the results of the analysis of N.E.'s thesis.

@@

    desc_table <-
      kbl(desc_met,
          caption = "Descriptive statistics of the questionnaire scores.",
          booktabs = T, # no vertical lines
          escape = F, # correctly print special characters
          align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
      kable_styling(latex_options = c("striped", "scale_down")) %>%
      footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
               escape = F, # correctly print special characters
               threeparttable = T) # line breaks in the footnote

@@

  corr_table <-
  kbl(correlations,
      caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

Basic metric descriptives of the questionnaire scores and subscales are listed in Table 1.
Only the ERQ sum score and its reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].

@@

Correlations and internal consistencies are displayed in Table 2.
For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman", exact = FALSE), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman", exact = FALSE), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman", exact = FALSE), format = "rmarkdown")`).
The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

@@

  replic_table <-
    kbl(replic_table,
        caption = "Results of the replication of Grass et al. (2018).",
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, \\beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

In order to replicate findings by Grass et al. [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates are displayed in Figure 1, total, direct, and indirect effects are listed in Table 3.
We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a2"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
Furthermore, even though NFC and reduced personal efficacy were both associated with self-control, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al. [-@Grass2018].

```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al. (2018). * $p<.05$, ** $p<.01$."}

@@

  replic_figure <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 26, sizeMan2 = 8, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
                       edge.label.cex = 1, esize = 2, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
We placed this variable as an independent variable influencing self control, as the latter was the only variable in the model that showed a partial correlation with years spent teaching.
As it was not preregistered, this was an exploratory analysis.
Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI=$ `r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates, total, direct, and indirect effects are displayed and listed in *Supplementary Material S3*.
The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the first model.
However, because of the positive association of years spent teaching and self control ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
Therefore, the total effect also increased slightly, compared to the first model ($\beta=$ `r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p=$ `r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).

@@

`r outliercorr_table`

@@

`r outlierreplic_table`
